Titeln på avhandlingens språk

### 2023-01-12 body/part1/overview/extending-wca.tex
writing

\subsubsection{Results}

@@

As mentioned before, we also found that the effects of system responsiveness on execution times lingered on after the system moved to a different level of impairment.
On average, the mean execution time of the first four steps of blocks were roughly \SI{10}{\percent} lower when the previous block was at a \ensuremath{TTF \leq \SI{2.475}{\second}} compared to when the previous block was at a \ensuremath{TTF > \SI{2.475}{\second}}.

Finally, analyses of the correlation between individual subject differences and the above effects highlighted the \gls{BFI} trait of \emph{neuroticism} as an important modulating factor.
This trait has been linked to low tolerance for stress, high emotional reactivity, as well as higher rates of \emph{delay discounting}~\cite{hirsh2008delay}.
Out of the three components identified by a \gls{PCA}, which cumulatively accounted for \textasciitilde\SI{73}{\percent} of the variance in the execution time results, neuroticism was present in the first two.
Furthermore, individual neuroticism scores were found to significantly linearly correlate (\ensuremath{rho = 0.418}, \num{2}-tailed \ensuremath{p < 0.05}) with measured execution times at high \glspl{TTF}.

>>>>

\subsubsection{Results}\label{impact:results}

@@

\begin{wrapfigure}{l}{.5\textwidth}
    \centering
    \includegraphics[height=13em]{figs/2021Impact/previousblock_vs_exectime}
    \caption{}\label{fig:prevblockvsexectime}
\end{wrapfigure}

As mentioned before, we also found that the effects of system responsiveness on execution times lingered on after the system moved to a different level of impairment.
\Cref{fig:prevblockvsexectime} illustrates this effect.
On average, the mean execution time of the first four steps of blocks was roughly \SI{7}{\percent} lower when the previous block was at a \ensuremath{TTF \leq \SI{2.475}{\second}} compared to when the previous block was at a \ensuremath{TTF > \SI{2.475}{\second}} (single-tailed \ensuremath{p < 0.001}).

Finally, analyses of the correlation between individual subject differences and the above effects highlighted the \gls{BFI} trait of \emph{neuroticism} as an important modulating factor.
This trait has been linked to low tolerance for stress, high emotional reactivity, as well as higher rates of \emph{delay discounting}~\cite{hirsh2008delay}.
Out of the three components identified by a \gls{PCA}, which cumulatively accounted for \textasciitilde\SI{73}{\percent} of the variance in the execution time results, neuroticism was present in the first two.
Furthermore, individual neuroticism scores were found to significantly linearly correlate (\ensuremath{rho = 0.418}, two-tailed \ensuremath{p < 0.05}) with measured execution times at high \glspl{TTF}.

\subsection{Extending the EdgeDroid tool with a realistic model of human behavior}

\cref{paper:olguinmunoz2023realistic} discusses the elaboration of a model of human behavior for \gls{WCA}.
Built upon the data and results from \cref{paper:olguinmunoz2021impact}, our model is capable of dynamically generating realistic predictions of execution times for steps in a \gls{WCA} based on historical system state data and a parameterized level of neuroticism.
Furthermore, we implement a new version of the EdgeDroid tool capable of using this new model, together with a novel procedure for the generation of realistic synthetic traces of frames for \gls{WCA}, to fully emulate a human in the context of these systems.

\subsubsection{Designing a realistic model for human timing ins \gls{WCA}}

As evidenced from the results of \cref{paper:olguinmunoz2021impact}, a model capable of generating realistic execution times for \gls{WCA} must take several things in consideration.
As discussed in \cref{impact:results}, the execution time for a step depends not only on the most recent perceived \gls{TTF}, but also on how long the system has been in the current level of responsiveness.
Additionally, as shown in \cref{fig:prevblockvsexectime}
